---
title: "Risk Analysis"
subtitle: "Productivity Analysis" 
author: "Laurie Kell & Alex Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r knitr, echo=FALSE}
library(knitr)

opts_chunk$set(comment=NA, fig.width =8, 
               fig.height=6,
               fig.path  ="../tex/",
               warning=FALSE, 
               message=FALSE, 
               error  =FALSE, 
               echo   =FALSE,
               cache  =TRUE)
iFig=0
iTab=0
```

```{r init}
library(ggplot2)
library(reshape2)

library(plyr)
library(dplyr)

library(FLCore)
library(FLife)
library(popbio)

library(ggthemes)
library(scales)

dirMy ="/home/laurence/Desktop/sea++/mydas/tasks"
dirInp=file.path(dirMy,"inputs")
dirDat=file.path(dirMy,"data")
 
theme_set(theme_bw())
```

## Fleets and gears (AT)

+ list all main gears in Celtic and North Sea
+ List all fisheries from a social economic view point

## PSA (AT)

Create a database with PSA parameters, including management and where possible economic values

### Productivity (LK)

+ get life history parameters for all stocks/spp
+ replicate Flavia et al.

```{r}
c("lmax","linf","t0","k","a50","amax","l50","fec","z/k","mort")
```

### Susceptibility (AT)

+ Quantitative estimates
    + availability (horizontal overlap) by gear and stock
    + encounterability (vertical overlap) by gear and stock
    + post capture mortality

+ Qualitative estimate
    + availability (horizontal overlap) by gear and stock
    + encounterability (vertical overlap) by gear and stock
    + post capture mortality

```{r}
c("stock","fleet","avail","encout")
c("stock","price","value")
```

### Management or Harvest Strategy (AT & LK)

Based on MSC

+ AT get assessment reports data together, 
+ LK goes through the assessments

### 1.2.1: Harvest Strategy
There is a robust and precautionary harvest strategy in place, i.e. target, threshold and limit reference 
points for F and biomass

### 1.2.2: Harvest Control Rules & Tools
There are well defined and effective harvest control rules (HCRs) in place, i.e. using ref pts to set TAC

### 1.2.3: Information/Monitoring
Relevant information is collected to support the harvest strategy, i.e which ICES catagory does the stock belong to?

### 1.2.4: Assessment of Stock Status 
There is an adequate assessment of the stock status, i.e. when was the stock last assessed and what method
 
```{r}
c("ftar","fthresh","flim","btar","bthresh","blim","cat","assyr","assmethod")
```

```{r}

```


```{r}
```
**Figure `r iFig=iFig+1; iFig`** .

# References

