---
title: "Management Procedure"
subtitle: "Biomass Dynamic"
author: "Laurence Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown:::html_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
bibliography: refs.bib
tags: FLPKG FLR
license: Creative Commons Attribution-ShareAlike 4.0 International
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(echo    =!TRUE,
               eval    =TRUE,
               cache   =FALSE,
               cache.path="cache/mp",
               prompt  =FALSE,
               comment =NA,
               message =FALSE,
               tidy    =FALSE,
               warning =FALSE,
               fig.height=4.5,
               fig.width =4.5,
               fig.path  ="tex/mp")
```


```{r, pkgs, echo=FALSE, message=FALSE}
library(ggplot2)

theme_set(theme_bw())
options(digits=3)
```

[](#top)

[Introduction](#Introduction)

[Installation](#Installation)

[Quick Start](#QuickStart)

[Harvest Control Rules](#Harvest)

[More information](#More)

[References](#References)

# Introduction {#Introduction}

In Management Strategy Evaluation (MSE) an Operating Model (OM) is used to simulate resource dynamics in trials in order to evaluate the performance of a Management Procedure (MP). Where the MP is the combination of pre-defined data, together with an algorithm to which such data are input to provide a value for a management control measure. 

The `mpb` package has various methods for developing MPs using a biomass dynamic stock assessment model.

[Back to Top](#top)

# Installation {#Installation}

The simplest way to obtain mpb is to install it from CRAN by using the following command in the R console:

```{r install,eval=FALSE}
install.packages("mpb", repos = "http://flr-project.org/R")
```

[Back to Top](#top)

# Quick Start {#QuickStart}

So that users may have a better idea of what functions are available, which one to choose, or where to seek help, this section provides a general overview of the package. In particular it highlights the various elements, what they do, and provides some examples of usage. More details are given in later sections.

First, load the `mpb` package:

```{r lib,echo=TRUE}
library(mpb)
library(plyr)
```


# Harvest Control Rules {#Harvest}

## fwd

```{r, fwd, echo=TRUE, eval=FALSE}
fwd(object, catch = NULL, harvest = NULL,
  stock = NULL, hcr = NULL, pe = NULL, peMult = TRUE, minF = 0,
  maxF = 2, bounds = list(catch = c(Inf, Inf)), lag = 0, end = NULL,
  starvationRations = 0.75, ...)
```

```{r, sim, echo=TRUE}
bd=sim()
```

```{r, projection, echo=TRUE}
bd=fwd(bd,catch=FLQuant(125,dimnames=list(year=49:100)))
```

```{r, projection2, echo=TRUE}
bd=fwd(bd,FLQuants("catch"  =FLQuant(125,dimnames=list(year=49:100)),
                   "harvest"=FLQuant(.35,dimnames=list(year=49:100))))

plot(bd)
```

```{r example1,echo=TRUE,eval=TRUE}
```


[Back to Top](#top)

# More information {#More}

* You can submit bug reports, questions or suggestions on `FLPKG` at the `FLPKG` issue page ^[<https://github.com/flr/FLPKG/issues>], or on the *FLR* mailing list.
* Or send a pull request to <https://github.com/flr/FLPKG/>
* For more information on the FLR Project for Quantitative Fisheries Science in R, visit the FLR webpage ^[<http://flr-project.org>].
* The latest version of `FLPKG` can always be installed using the `devtools` package, by calling
```{r, devtools, echo=TRUE, eval=FALSE}
	library(devtools)
	install_github('flr/FLPKG')
```


## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLPKG: `r # packageVersion('FLPKG')`
* **Compiled**: `r date()`
* **Git Hash**: `r system("git log --pretty=format:'%h' -n 1", intern=TRUE)`

## Author information

**Laurence KELL**. laurie.kell.es


## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}


[Back to Top](#top)
