---
title: "Mydas: Stock Assessments"
author: "Laurence Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown:::pdf_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
bibliography: /home/laurence/Desktop/sea++/cie/greySnapper/tex/refs.bib
tags: FLPKG FLR
license: Creative Commons Attribution-ShareAlike 4.0 International
---
\newpage 

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(echo    =FALSE,
               eval    =TRUE,
               cache   =!FALSE,
               cache.path="../cache/stocks/",
               prompt  =FALSE,
               comment =NA,
               message =FALSE,
               tidy    =FALSE,
               warning =FALSE,
               fig.height=6,
               fig.width =8,
               fig.path  ="../tex/a1-stocks-")

iFig=0
```
```{r, pkgs, echo=FALSE, message=FALSE}
library(plyr)
library(dplyr)
library(reshape2)
library(ggplot2)

library(FLCore)
library(FLBRP)
library(ggplotFL)
library(diags)
library(FLife)

options(digits=3)
```
```{r, dirs, echo=FALSE, message=FALSE}
dirMy=dirname(dirname(FLife:::getScriptPath()))
dirMy="/home/laurence/Desktop/sea++/mydas"
dirInp=file.path(dirMy,"inputs")
dirDat=file.path(dirMy,"data")
```

```{r, assessment, eval=FALSE}
nms=c("Cod North Sea", "Haddock North Sea","Whiting North Sea","Saithe North Sea", 
      "Plaice North Sea", "Sole North Sea",
      "Cod Celtic Sea","Haddock Celtic Sea","Whiting Celtic Sea")
spp=c("Gadus morhua","Melanogrammus aeglefinus","Merlangius merlangus",
      "Pleuronectes platessa","Solea solea")
spp=spp[c(1:6,1:3)]
sea=c(rep("North Sea",6),rep("Celtic Sea",3))
stock=c("cod347","hadns","whg3747d","ple27420","solnsea","sains",
        "cod7ek","whg7bk","hadcs")
nms=data.frame(nms,spp,sea,stock)

load("/home/laurence/Desktop/sea++/stecf/data/stk.RData")
stk=stk["hadns"]

load("/home/laurence/Desktop/sea++/stecf/inputs/nsea/cod347/cod347_FLStockObject_wgnssk17_nscod17_ass06.RData")
stk["codns"]=cod

load("/home/laurence/Desktop/sea++/stecf/inputs/nsea/whg3747d/whg.27.47d.stock.Rdata")
stk["whgns"]=x.stock

load("/home/laurence/Desktop/sea++/stecf/inputs/nsea/ple27420/ple27.7d_stockobject.Rdata")
stk["plens"]=ass.stock

load("/home/laurence/Desktop/sea++/stecf/inputs/nsea/solns/sol-nsea_ass.stock_workspace.Rdata")
stk["solns"]=ass.stock

load("/home/laurence/Desktop/sea++/mydas/inputs/ns/ple27420/ple.27.420_stock.object.Rdata")
stk["sains"]=ass.stock

load("/home/laurence/Desktop/sea++/mydas/inputs/cs/cod7ek/xsa.stock.Rdata")
stk["codcs"]=xsa.stock

load("/home/laurence/Desktop/sea++/mydas/inputs/cs/whg7bk/xsa.Rdata")
stk["whgcs"]=stock

load("/home/laurence/Desktop/sea++/mydas/inputs/cs/colm/HAD_stock.RData")
stk["hadcs"]=stock

stk=llply(stk[c("codns","hadns","sains","whgns","plens","solns","codcs","hadcs","whgcs")],
                   function(x) iter(x,1))

save(nms,file=file.path(dirDat,"nms.RData"),compress="xz")
save(stk,file=file.path(dirDat,"stk.RData"),compress="xz")
```

```{r, indices, eval=FALSE}
load("/home/laurence/Desktop/sea++/mydas/inputs/ns/ple27420/ple.27.420_stock.object.Rdata")
idxs=list("solns"=indices)

load("/home/laurence/Desktop/sea++/mydas/inputs/cs/cod7ek/cod_idx.RData")
idxs["codcs"]=idx

load("/home/laurence/Desktop/sea++/mydas/inputs/cs/colm/HAD_tunning.RData")
idxs["hadcs"]=tun

load("/home/laurence/Desktop/sea++/mydas/inputs/cs/colm/PLE_tun.Rdata")
idxs["plecs"]=tun

load("/home/laurence/Desktop/sea++/mydas/inputs/cs/sol7fg/INPUT/sol7fg_stock.Rdata")
idxs["solcs"]=tun

idxs=idxs[c("solns","codcs","hadcs","plecs","solcs")]
idx=idxs

save(idx,file=file.path(dirDat,"idx.RData"),compress="xz")
```

```{r, stk-ts}
load(file.path(dirDat,"stk.RData"))

stkTs=ldply(stk,
          function(x) 
              model.frame(FLQuants(
                ssb    =ssb( x),
                f      =fbar(x),
                catch  =catch(x),
                cpue   =catch(x)%/%fbar(x),
                recruit=rec(x),
                stock  =stock(x),
                hrate  =catch(x)%/%stock(x),
                pgwt   =stock.n(x)[ac(range(x)["plusgroup"])]%*%stock.wt(x)[ac(range(x)["plusgroup"])],
                pgn    =stock.n(x)[ac(range(x)["plusgroup"])],
                cmnwt  =FLQuant(aaply(catch.n(x)%*%catch.wt(x),2:6,sum))%/%
                            FLQuant(aaply(catch.n(x),2:6,sum)),
                smnwt  =FLQuant(aaply(stock.n(x)%*%stock.wt(x),2:6,sum))%/%
                            FLQuant(aaply(stock.n(x),2:6,sum)),
                cmnage =FLQuant(aaply(catch.n(x)%*%ages(catch.wt(x)),2:6,sum))%/%
                            FLQuant(aaply(catch.n(x),2:6,sum)),
                smnage =FLQuant(aaply(stock.n(x)%*%ages(stock.wt(x)),2:6,sum))%/%
                            FLQuant(aaply(stock.n(x),2:6,sum))
                ),drop=TRUE))
save(stkTs,file=file.path(dirDat,"stkTs.RData"))
```

```{r, ssb}
ggplot(stkTs)+
  geom_line(aes(year,ssb,col=.id))+
  guides(colour=guide_legend(title="Stock",title.position="left"))+
  xlab("Year")+ylab("SSB")+
  theme_bw()+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1; paste("A1.",iFig,sep="")`**


```{r, harvest}
ggplot(stkTs)+
  geom_line(aes(year,f,col=.id))+
  guides(colour=guide_legend(title="Stock",title.position="left"))+
  xlab("Year")+ylab("F")+
  theme_bw()+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1; paste("A1.",iFig,sep="")`**

```{r, yield}
ggplot(stkTs)+
  geom_line(aes(year, catch,col=.id))+
  guides(colour=guide_legend(title="Stock",title.position="left"))+
  xlab("Year")+ylab("Catch")+
  theme_bw()+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1; paste("A1.",iFig,sep="")`**


```{r, ce}
ggplot(stkTs)+
  geom_line(aes(year,cpue,col=.id))+
  guides(colour=guide_legend(title="Stock",title.position="left"))+
  xlab("Year")+ylab("CPUE")+
  theme_bw()+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1; paste("A1.",iFig,sep="")`**

```{r, rec}
ggplot(stkTs)+
  geom_line(aes(year,recruit,col=.id))+
  guides(colour=guide_legend(title="Stock",title.position="left"))+
  xlab("Year")+ylab("Recruitment")+
  theme_bw()+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1; paste("A1.",iFig,sep="")`**


```{r, biomass}
ggplot(stkTs)+
  geom_line(aes(year,stock,col=.id))+
  guides(colour=guide_legend(title="Stock",title.position="left"))+
  xlab("Year")+ylab("Biomass")+
  theme_bw()+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1; paste("A1.",iFig,sep="")`**

```{r, hrate}
ggplot(stkTs)+
  geom_line(aes(year,hrate,col=.id))+
  guides(colour=guide_legend(title="Stock",title.position="left"))+
  xlab("Year")+ylab("Harvest Rate")+
  theme_bw()+
  theme(legend.position="bottom")
```
**Figure `r iFig=iFig+1; paste("A1.",iFig,sep="")`**


```{r}
load(file.path(dirDat,"idx.RData"))

x1=ldply(idx[c(1,1)], function(x) ldply(x, function(y) as.data.frame(index(y),drop=TRUE)))
x2=ldply(idx[-1], function(y) as.data.frame(index(y),drop=TRUE))
```

\newpage
## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLife:  `r packageVersion('FLife')`
* FLBRP:  `r packageVersion('FLBRP')`
* **Compiled**: `r date()`

## Author information

**Laurence KELL**. laurie@kell.es

# References {#References}

