---
title: "Cross test using Operating Model based on Life History"
subtitle: "LBSPR, length based assessment"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{FLife}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
github_document:
    mathjax: TRUE
tags: FLife
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =TRUE,
               cache.path="../cache/crosstest/lbspr/",
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=6,
               fig.width =8,
               fig.path  ="../tex/FLife-OM-lbspr")

options(digits=3)

iFig=0
```
```{r pkgs}
library(plyr)
library(reshape)
library(ggplot2)
library(dplyr)

library(FLCore)
library(ggplotFL)
library(FLRP)
library(FLife)

library(LBSPR)
```
```{r, dir}
dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task5"
dirDat=file.path(dirMy,"data")
```
```{r, dat}
load(file.path(dirDat,"brill.RData"))
```

## OM
```{r, om}
plot(om)
```
**Figure `r iFig=iFig+1; iFig`** Operating model for Brill. 


## OEM
```{r, oem}
# Length frequency distribution
om1=window(iter(om,1),start=21,end=100)

n  =catch.n(om1)
ln =vonB(ages(catch.n(om1)),iter(lh,1))
sd =ln*0.2
bin=0:ceiling(max(ln)*1.10)+0.5

### Create lengths-at-age 
lfq=ddply(model.frame(FLQuants(ln=ln,sd=sd,n=n)),.(age,year,unit,season,area,iter), 
           with, data.frame(length=bin,data=dnorm(bin,ln,sd)*n))
  
### sum up by length 
lfq=ddply(lfq,.(length,year,unit,season,area,iter), 
           with, data.frame(freq=sum(data)))
```


```{r, oemplot}
ggplot(subset(lfq,year %in% seq(50,100,5)))+
  geom_histogram(aes(length,weight=freq),binwidth=1)+
  facet_grid(year~.,scale="free")+
  xlab("Length (cm)")+ylab("Frequency")
```

**Figure `r iFig=iFig+1; iFig`** Catch size data . 


## MP

```{r}
lbspr<-function(len,params,species="",units="cm"){

  pars        =new("LB_pars")
  pars@Linf   =c(params["linf"]) 
  pars@L50    =vonB(c(params["a50"]),params) 
  pars@L95    =pars@L50+vonB(c(params["ato95"]),params)
  pars@MK     =c(params["mk"])
  pars@Species=species
  pars@L_units=units
  
  #labs=dimnames(len)[[1]]
  #brks=cbind(lower = as.numeric( sub("\\((.+),.*", "\\1", labs) ),
  #           upper = as.numeric( sub("[^,]*,([^]]*)\\]", "\\1", labs) ))
  #mid=aaply(brks,1,mean)
  
  LBlen       =new("LB_lengths")
  LBlen@LMids =as.numeric(dimnames(len)[[1]])
  LBlen@LData =len
  LBlen@Years =as.numeric(dimnames(len)[[2]])
  LBlen@NYears=dim(len)[2] 
  
  LBSPRfit(pars,LBlen)}
```

```{r, fm}
len=t(daply(lfq,.(year,length), with, sum(freq)))
brl=lbspr(len,prior[,1])

save(brl,file="/home/laurence/Desktop/tmp/brl.RData")
ggplot(data.frame("Year"=21:100,
               "MP"=brl@Ests[,"FM"],
               "OM"=c(apply(harvest(om[,ac(21:100)])%/%m(om[,ac(21:100)]),c(2),mean))))+
  geom_line(aes(Year,OM),col="red")+
  geom_line(aes(Year,MP))
```
**Figure `r iFig=iFig+1; iFig`** Comparison of estimated and actual $F/M$ ratios.

```{r, spr}
ggplot(data.frame("Year"=21:100,
               "MP"=brl@Ests[,"SPR"],
               "OM"=c(apply(ssb(om[,ac(21:100)])%/%rec(om[,ac(21:100)]),c(2),mean))/1000))+
  geom_line(aes(Year,OM),col="red")+
  geom_line(aes(Year,MP))
```
**Figure `r iFig=iFig+1; iFig`** Estimated SPR.

\newpage
## Session Info

```{r}
sessionInfo()
```

## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLife:  `r packageVersion('FLife')`
* FLRP:  `r packageVersion('FLRP')`
* **Compiled**: `r date()`

## Author information

**Laurence KELL**. laurie@kell.es

# References {#References}

