---
title: "Cross test using Operating Model based on Life History"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{FLife}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
github_document:
    mathjax: TRUE
tags: FLife
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---

```{r knitr_init, echo=FALSE, results="hide"}
library(knitr)
## Global options
opts_chunk$set(cache     =TRUE,
               cache.path="../cache/crosstest/",
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=6,
               fig.width =8,
               fig.path  ="../tex/FLife-OM-")

options(digits=3)

iFig=0
```
```{r pkgs}
library(plyr)
library(popbio)

library(FLCore)
library(ggplotFL)
library(FLife)
```
```{r, dir}
dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task5"
dirDat=file.path(dirMy,"data")
```
```{r, dat}
load(file.path(dirDat,"brill.RData"))
```

## OEM
```{r, cpue, echo=TRUE, eval=TRUE}
setGeneric("cpue", function(object, ...) standardGeneric("cpue"))

#' @rdname cpue
#' @aliases cpue,FLStock-method
setMethod('cpue',   signature(object='FLStock'),
  function(object, sel=catch.sel(object), effort = c("f","h"), mass = TRUE) {

    if (effort[1] == "h")
      E <- catch(object) %/% stock(object)
    else  
      E <- fbar(object)
    
    cpue <- (catch.n(object) %*% sel) %/% E

  if (mass)
    cpue <- cpue * catch.wt(object)

  return(cpue)
  }
)
```

```{r, survey, echo=TRUE, eval=TRUE}
# survey
setGeneric("survey", function(object, ...) standardGeneric("survey"))

setMethod("survey",   signature(object="FLStock"),
  function(object, sel=stock.n(object) %=% 1, wt=stock.wt(object), timing=0.5, mass=FALSE) {
  
    timing=pmax(pmin(timing, 1.0), 0.0)

    stock.n=stock.n(object)*exp(-(harvest(object)*timing+m(object)*timing))
 
    res=stock.n%*%sel
  
    if (mass)
       res=res%*%wt

  return(res)})
```

```{r, size, echo=TRUE, eval=TRUE}
#### Indicators ################################################################
setGeneric("mnSwt", function(object,...)
   standardGeneric("mnSwt"))
setGeneric("mnCwt", function(object,...)
   standardGeneric("mnCwt"))
setGeneric("mnLwt", function(object,...)
   standardGeneric("mnLwt"))
setGeneric("mnLen", function(object,...)
   standardGeneric("mnLen"))
setGeneric("wt2z", function(object,...)
   standardGeneric("wt2z"))
setGeneric("ln2z", function(object,Linf,...)
    standardGeneric("ln2z"))

setMethod('mnSwt', signature(object='FLStock'), function(object) apply(stock.wt(   object)*stock.n(   object),2:6,sum)/apply(stock.n(   object),2:6,sum)) 
setMethod('mnCwt', signature(object='FLStock'), function(object) apply(catch.wt(   object)*catch.n(   object),2:6,sum)/apply(catch.n(   object),2:6,sum)) 
setMethod('mnLwt', signature(object='FLStock'), function(object) apply(landings.wt(object)*landings.n(object),2:6,sum)/apply(landings.n(object),2:6,sum)) 
  
setMethod('mnLen', signature(object='FLStock'), 
    function(object,a=0.001,b=3,wt="stock.wt") 
    mnLenFunc(object,a,b,wt))
setMethod('wt2z', signature(object='FLStock'), 
    function(object,a=0.001,b=3,wt="stock.wt") 
          wt2zFunc(object,a,b,wt))
setMethod('ln2z', signature(object='numeric',Linf='numeric'),
    function(object,Linf,Lc,k) 
	  ln2zFunc(object,Linf,Lc,k))
setMethod('ln2z', signature(object='numeric',Linf="FLPar"),
    function(object,Linf) 
	  ln2zFunc(object,Linf["Linf"],Linf["Lc"],Linf["k"]))

mnLenFunc<-function(object,a=0.001,b=3,wt="stock.wt"){
    wt.=slot(object,wt)
    n. =slot(object,gsub(".wt",".n",wt))

    apply((wt./a)^(1/b)*n.,c(2,6),sum)/apply(n.,c(2,6),sum)}

wt2zFunc<-function(object,Linf,Lc,k,a=0.001,b=3,wt="stock.wt"){
    mnSz<-mnSzStock(object,a,b,wt); 
    k*(Linf-mnSz)/(mnSz-Lc)}

ln2zFunc<-function(object,Linf,Lc,k){
    k*(Linf-object)/(object-Lc)}
################################################################################
```

```{r, hyperstability, eval=TRUE}
hyperstability<-function(object,omega=1,ref=apply(object,c(1,3:6),mean)) 
  ref%*%((object%/%ref)^omega)
```

```{r, trend, eval=TRUE}
trend<-function(object,bias=0.02) 
  FLQuant(cumprod(1+rep(bias,dim(object)[2])),dimnames=dimnames(object))
```

```{r, om}
theme_set(theme_bw())
plot(om)
```

**Figure `r iFig=iFig+1; iFig`,** Operating Model Time series.

```{r, oem-srvy}
set.seed(1234)
om1=iter(om,1)
u     =FLQuants("Unbiased"      =rlnorm(100,log(apply(survey(om1),2:6,sum)),.3),
                "Hyperstability"=rlnorm(100,log(apply(survey(om1),2:6,sum)%*%
                                                  hyperstability(stock(om1),0.5)),.3),
                "Hyperdepletion"=rlnorm(100,log(apply(survey(om1),2:6,sum)%*%
                                                  hyperstability(stock(om1),1.5)),0.3),
                "Trend"         =rlnorm(100,log(apply(survey(om1),2:6,sum)%*%bias(stock(om1),0.02)),.3),
                "AR"            =apply(survey(om1),2:6,sum)%*%
                                   exp(rnoise(100,apply(survey(om1),2:6,sum)*0,.3,b=.7)),
                "Juvenile"      =rlnorm(100,log(apply(survey(om1,sel=mat(om1)),2:6,sum)),.3),
                "Mature"        =rlnorm(100,log(apply(survey(om1,sel=1-mat(om1)),2:6,sum)),.3),
                "Numbers"       =rlnorm(100,log(apply(survey(om1,mass=FALSE),2:6,sum)),.3))

u=FLQuants(llply(u,function(x) x/mean(x)))
u=ldply(u,as.data.frame)

u.=ddply(u,.(year,.id), with, quantile(data))
ggplot()+
  geom_line(aes(year,data,col=factor(iter)),
            data=subset(u,iter%in%c(23,11)))+
  geom_ribbon(aes(year,ymin=`25%`,ymax=`75%`),data=u.,col="grey",alpha=.5)+
  facet_wrap(~.id,ncol=2)+
  theme_bw()+theme(legend.position="none")
```

**Figure `r iFig=iFig+1; iFig`,** Commercial indices of abundance.


```{r, oem-com}
set.seed(1234)
om1=iter(om,1)
u     =FLQuants("Unbiased"      =rlnorm(100,log(apply(cpue(om1),2:6,sum)),.3),
                "Hyperstability"=rlnorm(100,log(apply(cpue(om1),2:6,sum)%*%
                                                  hyperstability(stock(om1),0.5)),.3),
                "Hyperdepletion"=rlnorm(100,log(apply(cpue(om1),2:6,sum)%*%
                                                  hyperstability(stock(om1),1.5)),0.3),
                "Trend"         =rlnorm(100,log(apply(cpue(om1),2:6,sum)%*%bias(stock(om1),0.02)),.3),
                "AR"            =apply(cpue(om1),2:6,sum)%*%
                                   exp(rnoise(100,apply(cpue(om1),2:6,sum)*0,.3,b=.7)),
                "Juvenile"      =rlnorm(100,log(apply(cpue(om1,sel=mat(om1)),2:6,sum)),.3),
                "Mature"        =rlnorm(100,log(apply(cpue(om1,sel=1-mat(om1)),2:6,sum)),.3),
                "Numbers"       =rlnorm(100,log(apply(cpue(om1,mass=FALSE),2:6,sum)),.3))

u=FLQuants(llply(u,function(x) x/mean(x)))
u=ldply(u,as.data.frame)

u.=ddply(u,.(year,.id), with, quantile(data))
ggplot()+
  geom_line(aes(year,data,col=factor(iter)),
            data=subset(u,iter%in%c(23,11)))+
  geom_ribbon(aes(year,ymin=`25%`,ymax=`75%`),data=u.,col="grey",alpha=.5)+
  facet_wrap(~.id,ncol=2)+
  theme_bw()+theme(legend.position="none")
```

**Figure `r iFig=iFig+1; iFig`,** Survey indices of abundance.

```{r, oem-size}
theme_set(theme_bw())

plot(mnLen(om))
```

**Figure `r iFig=iFig+1; iFig`,** Index of mean length.

## Priors


Lmax	Amax	Selectivity (S50; S95)	K or B0	r	Lc	Lopt	k	Linf	to	Lm50	A50	M	h	alpha-B-H	M/K	Fmsy/M	Fmsy/K	Bmsy/K (or B0)	Depletion	Fecundity at age/length	Length-weight relationship

```{r}
lh[c("linf","k","t0","a50","ato95","a","b","s","v")]
rf=FLPar(refpts(eq)["msy",c("harvest","yield","ssb"),drop=T])
names(rf)[1]="params"
dimnames(rf)[[1]]=c("fmsy","msy","bmsy")

rbind(lh,rf)

#lopt
lopt(lhPar(lh),growth=vonB)

#lc
vonB(alh["a50"]-lh["ato95"],lh)

maply(seq(dims(eq)[6]), function(x) lamba(leslie(iter(eq,x),fbar=c(refpts(eq)["crash","harvest"]))[drop=TRUE]))

#"fmsy/m"
eq@fbar=fbar(eq)[,1]
eq@fbar[]=refpts(eq)["msy","harvest"]

apply(fbar(eq)%/%m(eq),6,mean)

#"m/k",
apply(m(eq),6,mean)

#"fmsy/k",

#"bmsy/K"
```


# Stock Assessment Models

## Catch only


### DB-SRA: Depletion-based Stock reduction analysis (Dick and MacCall 2011)

data catch only

parameters: a50, m, Fmsy/m, bmsy/k, depletion

outputs: K, B0, bmsy, fmsy, msy Cfmsy

## Length

### lbspr

data length

paramters linf, m/k, W=al^b

outputs

F/M, selectivilty at length, SPR

## Catch and Cpue

biodyn


